Proposal full title \\ Proposal Acronym

### 2001-10-15 drafts/IST/PartA.tex
ALERT
svn path=/trunk/; revision=1509
Switched from NAME to SICHA.
svn path=/trunk/; revision=1549

Proposal Acronym &  \\ \hline
Proposal Number &  \\ \hline

@@

Proposal full name & \\ \hline

@@

The NAME project will provide a generic solution that can be used and adapted
by all of them.  NAME will of course provide the same services as current

@@

NAME will also provide support for internationalization to help dissemination
and adoption in European countries for non english speakers.\\ Finally NAME

@@

Duration in months & \\ \hline

@@

The NAME project aims at developping a complete hosting facility. It is 

@@

To achieve this goal, we will 
1 redesing existing hosting architectures such as Savannah and Picolibre 
  so that they may be packaged, installed and taylored easily; 
2 integrate multilanguage support to these platforms and implement support
  versions for portuguese, german, spanish, english and french;
3 define common data types and representation between the two types of
  platform with possible interaction with other platform via the CoopX project;
4 introduce functionalities to import/export informations from one site to
  another, based on this common data representation;
5 test and deploy over wide area network at least three sites in three out
	of four participating countries.
%1445/1224 chars need check and more description
\subsection*{Milestones and expected result (max 500 characters)}
PM 3: specification of new hosting architecture
PM 6: specification of common data formats
PM 9: V1 of savannah with new design 1 language version
PM12: V1 of picolibre with new design
      V2 of savannah with support for at least 2 languages and import/export
PM15: V2 of picolibre with multilingual support for at least 2 languages and
      import/export functionalities
PM18: deployment of redesigned platform in 3 countries, 
      dissemination of the project results by a Debian package.
%496/408
\section*{A4 Cost Summary}
%% will look at that later
\rotatebox{90}{
\begin{tabular}{c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|}
Participant Role(CO/P) & Participant Number & Linked to Contractor No &
Participant Short Name & Number of Person - Months & Personnel Costs &
Durable Equipment & Consumables & Travel and subsitence & Computing &
External assistance & Other Costs & Knowledge protection on Costs & 
Overhead Costs & Total Costs & Requested Contribution from the Commision &
Eligibility (Y/No)\\
\end{tabular}
}
\end{document}

>>>>

Proposal Acronym &  SICHA \\ \hline
Proposal Number &  ??????? \\ \hline

@@

Proposal full name & Simple International Cooperative Hosting Architecture \\ \hline

@@

The SICHA project will provide a generic solution that can be used and adapted
by all of them.  SICHA will of course provide the same services as current

@@

SICHA will also provide support for internationalization to help dissemination
and adoption in European countries for non english speakers.\\ Finally SICHA

@@

Duration in months & ?????? \\ \hline

@@

The SICHA project aims at developping a complete hosting facility. It is 

@@

To achieve this goal, we will 
1 redesing existing hosting architectures such as Savannah and Picolibre 
  so that they may be packaged, installed and taylored easily; 
2 integrate multilanguage support to these platforms and implement support
  versions for portuguese, german, spanish, english and french;
3 define common data types and representation between the two types of
  platform with possible interaction with other platform via the CoopX project;
4 introduce functionalities to import/export informations from one site to
  another, based on this common data representation;
5 test and deploy over wide area network at least three sites in three out
	of four participating countries.
%1445/1224 chars need check and more description
\subsection*{Milestones and expected result (max 500 characters)}
PM 3: specification of new hosting architecture
PM 6: specification of common data formats
PM 9: V1 of savannah with new design 1 language version
PM12: V1 of picolibre with new design
      V2 of savannah with support for at least 2 languages and import/export
PM15: V2 of picolibre with multilingual support for at least 2 languages and
      import/export functionalities
PM18: deployment of redesigned platform in 3 countries, 
      dissemination of the project results by a Debian package.
%496/408
\section*{A4 Cost Summary}
%% will look at that later
\textbf{This must be discussed very soon}
\rotatebox{90}{
\begin{tabular}{c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|}
Participant Role(CO/P) & Participant Number & Linked to Contractor No &
Participant Short Name & Number of Person - Months & Personnel Costs &
Durable Equipment & Consumables & Travel and subsitence & Computing &
External assistance & Other Costs & Knowledge protection on Costs & 
Overhead Costs & Total Costs & Requested Contribution from the Commision &
Eligibility (Y/No)\\
\end{tabular}
}
\end{document}

### 2001-10-15 drafts/IST/PartB.tex
Switched from NAME to SICHA.
svn path=/trunk/; revision=1549

more info : http://www.cordis.lu/ist/bwp_en5.htm
\end{verbatim}
\maketitle
\tableofcontents
\chapter*{B3. Objectives}
\addcontentsline{toc}{chapter}{B3. Objectives}
\textit{This section, which should not exceed two pages, describes the
scientific/technological objectives of the proposal. They should be achievable
within the project, not through subsequent development, and should be stated in
a measurable and verifiable form. The Progress of the Take-Up action will be
measured against theses objectives in later reviews and assessments.\\
This section should clearly specify in addition to the technical objectives -
also the quantified business objectives and how they are measured}
\\ \\
\section*{Decentralized.}
Any given machine running NAME can host a list of
projects (with pointers to the machines hosting the
projects), read-only copies of projects (with pointers
to the machines hosting the read-write instance of the
project), read-write projects.
\\
The read-only projects are mirrored from the machine
hosting the read-write instance of the project or other
machines hosting a read-only copy. The format used is
based on XML and defined by CoopX (http://coopx.eu.org).
\\
The number of read-only and read-write projects hosted
on a given machine is controlled by the maintainer of the
machine, depending on the available resources. For instance,
an average machine with lots of bandwidth could host at most
one hundred read-write projects and ten thousand read-only
projects.
\\
At a given time, only one machine hosts a read-write
project. It is the responsibility of the project
maintainers to ensure this.  Should a machine become
unavailable for some reason, the administrators of the
project can toggle the read-only flag of one of the
read-only mirrors and start using it as a
replacement. 
\\
Such a decentralized setup is not the most efficient
replication system but it is definitely simple and
requires very little effort.
The first objective is to build a code base with all tools that current hosting
facilities have. The first audit we made shows there are a Bug tracking system,
per project mailing lists and web forums, project management tools

\section*{Multi machine.}
A single machine may not be powerful enough for someone
willing to host a large number of projects. Planning a
multi machine setup in advance is mostly impossible
because many strategies can be implemented depending on
the needs. For instance a site like SourceForge will not
implement the same strategies than a site like Geocities
because the usage pattern is not the same.
\\
A Debian package repository will be used to store the
packages that implement various strategies. They can all
coexist together. Let's say, for instance, that the
package NAME-single implements a single machine setup
and depends on exim, cvs and bind. There can also be a
NAME-multi-cvs, NAME-multi-exim, NAME-multi-bind,
each installed on a separate machine and that configure
the corresponding service for a multi-machine setup.

@@

Every bit is packaged for Debian. Although it may be
desirable to package it for other GNU/Linux distributions,
this is not our goal. The cooperative nature of Debian and
the package dependency management are essential. When the
set of packages reach a stable state it will be possible
to contribute them to Debian without a need to find an
agreement with a company. The dependency management allows
to consistently use a large set of packages.
\\
The packages will be produced in a source specific to the
project. This source will contain three types
of packages: copy of existing Debian packages slightly modified
for the needs of NAME, packages of unfinished software written
for NAME, packages whose sole purpose is to bind a set of 
packages together and configure them. 
\\
The software specific to NAME will be packaged at a very
early stage. Basically the package will be done whenever the
software performs at least one task. Properly packaging a
software takes a lot of time and failing to do it from the
very beginning is asking for troubles. It also allows
developpers to use the software and contribute to it in an
organized way. Finally, since NAME is a collection of
many packages it allows to debug and architecture their
interdepencies while writing code.

@@

Each release provides an upgrade procedure from the
previous version. The upgrade may imply a planned
down-time, NAME is commited to provide an upgrade
facility that would work without stopping the service. The
XML dump of the database will be used to upgrade the data
using XSL files. The database structure itself is upgraded
with a set of SQL orders. The associated services (smtp,
cvs, etc.) are reset to their initial state (empty) and
the backend scripts are run on the upgraded database to
restore the desired state.

@@

CoopX provides a set of XML based schemas to represent all
the data related to a project. This includes the description
of a user (P3P), contact information (XMLvCard) and custom
made schemas for the CVS tree and the bug tracker information
for instance. 
\\
The goal of CoopX is not to promote a standard but to use
them where possible. The bug tracker information, for
instance, is codified using a DTD with some documentation
to understand it.  There are no plans to submit it to W3C
or other similar organizations.
\\
The CoopX format is used for upgrades and for communication
between distinct NAME platforms.

@@

%% DRAFT, be nice :-) . GM
The NAME project completely follows the '' Take up Action `` second objective.
Indeed, it is designed to allow anybody even with limited ressources to install
a development for free software. Therefore, even smallest projects will have a
complete platform which will use the generic interfaces available on bigger
sites. Furthermore, free software related organizations will have a complete
packaged solution to provide all the needed tools for development. Since the
project is completely distributed, it will have little architecture
requirements and then will be easy to integrate into an existing network.
\\ \\

>>>>

more info : http://www.cordis.lu/ist/bwp_en5.htm
\end{verbatim}
\maketitle
\tableofcontents
\chapter*{B3. Objectives}
\addcontentsline{toc}{chapter}{B3. Objectives}
\textit{This section, which should not exceed two pages, describes the
scientific/technological objectives of the proposal. They should be achievable
within the project, not through subsequent development, and should be stated in
a measurable and verifiable form. The Progress of the Take-Up action will be
measured against theses objectives in later reviews and assessments.\\
This section should clearly specify in addition to the technical objectives -
also the quantified business objectives and how they are measured}
\\ \\
\section*{Decentralized.}
Any given machine running SICHA can host a list of
projects (with pointers to the machines hosting the
projects), read-only copies of projects (with pointers
to the machines hosting the read-write instance of the
project), read-write projects.
\\
The read-only projects are mirrored from the machine
hosting the read-write instance of the project or other
machines hosting a read-only copy. The format used is
based on XML and defined by CoopX (http://coopx.eu.org).
\\
The number of read-only and read-write projects hosted
on a given machine is controlled by the maintainer of the
machine, depending on the available resources. For instance,
an average machine with lots of bandwidth could host at most
one hundred read-write projects and ten thousand read-only
projects.
\\
At a given time, only one machine hosts a read-write
project. It is the responsibility of the project
maintainers to ensure this.  Should a machine become
unavailable for some reason, the administrators of the
project can toggle the read-only flag of one of the
read-only mirrors and start using it as a
replacement. 
\\
Such a decentralized setup is not the most efficient
replication system but it is definitely simple and
requires very little effort.
The first objective is to build a code base with all tools that current hosting
facilities have. The first audit we made shows there are a Bug tracking system,
per project mailing lists and web forums, project management tools

\section*{Multi machine.}
A single machine may not be powerful enough for someone
willing to host a large number of projects. Planning a
multi machine setup in advance is mostly impossible
because many strategies can be implemented depending on
the needs. For instance a site like SourceForge will not
implement the same strategies than a site like Geocities
because the usage pattern is not the same.
\\
A Debian package repository will be used to store the
packages that implement various strategies. They can all
coexist together. Let's say, for instance, that the
package SICHA-single implements a single machine setup
and depends on exim, cvs and bind. There can also be a
SICHA-multi-cvs, SICHA-multi-exim, SICHA-multi-bind,
each installed on a separate machine and that configure
the corresponding service for a multi-machine setup.

@@

Every bit is packaged for Debian. Although it may be
desirable to package it for other GNU/Linux distributions,
this is not our goal. The cooperative nature of Debian and
the package dependency management are essential. When the
set of packages reach a stable state it will be possible
to contribute them to Debian without a need to find an
agreement with a company. The dependency management allows
to consistently use a large set of packages.
\\
The packages will be produced in a source specific to the
project. This source will contain three types
of packages: copy of existing Debian packages slightly modified
for the needs of SICHA, packages of unfinished software written
for SICHA, packages whose sole purpose is to bind a set of 
packages together and configure them. 
\\
The software specific to SICHA will be packaged at a very
early stage. Basically the package will be done whenever the
software performs at least one task. Properly packaging a
software takes a lot of time and failing to do it from the
very beginning is asking for troubles. It also allows
developpers to use the software and contribute to it in an
organized way. Finally, since SICHA is a collection of
many packages it allows to debug and architecture their
interdepencies while writing code.

@@

Each release provides an upgrade procedure from the
previous version. The upgrade may imply a planned
down-time, SICHA is commited to provide an upgrade
facility that would work without stopping the service. The
XML dump of the database will be used to upgrade the data
using XSL files. The database structure itself is upgraded
with a set of SQL orders. The associated services (smtp,
cvs, etc.) are reset to their initial state (empty) and
the backend scripts are run on the upgraded database to
restore the desired state.

@@

CoopX provides a set of XML based schemas to represent all
the data related to a project. This includes the description
of a user (P3P), contact information (XMLvCard) and custom
made schemas for the CVS tree and the bug tracker information
for instance. 
\\
The goal of CoopX is not to promote a standard but to use
them where possible. The bug tracker information, for
instance, is codified using a DTD with some documentation
to understand it.  There are no plans to submit it to W3C
or other similar organizations.
\\
The CoopX format is used for upgrades and for communication
between distinct SICHA platforms.

@@

%% DRAFT, be nice :-) . GM
The SICHA project completely follows the '' Take up Action `` second objective.
Indeed, it is designed to allow anybody even with limited ressources to install
a development for free software. Therefore, even smallest projects will have a
complete platform which will use the generic interfaces available on bigger
sites. Furthermore, free software related organizations will have a complete
packaged solution to provide all the needed tools for development. Since the
project is completely distributed, it will have little architecture
requirements and then will be easy to integrate into an existing network.
\\ \\

### 2001-10-15 drafts/IST/PartC.tex
Switched from NAME to SICHA.
svn path=/trunk/; revision=1549

To ensure the NAME project dissemination it will be packaged so that 

@@

\chapter*{C4. Contribution to Community social objectives}
\addcontentsline{toc}{chapter}{C4. Contribution to Community social objectives}
\textit{This section, not exceeding two pages, should describe how the proposed
subject wil contribute to meeting the social objectives of the Community, and
should focus on the contribution of the project to improving employment
prospects and the use and development of skills in Europe. \\
Where aplicable the descriptions should also cover how the proposed measure
contributes to improving quality of life and health and safety (including
working condition), and/or to preserving or enhancing the environment and
natural ressources. This might include the contribution of the proposed work to
meeting relevant regulatory requirements.}
\\ \\
The NAME project will help in creating more free/open software in EU by easing 
the access to a software hosting project platform.
\\
The software created using the hosting platforms, resulting from the NAME 
project, will help reduce the software costs for individuals as well as for
small companies and large industrial groups. 
\\
The NAME project will also strengthen existing software by allowing more 
developpers and testers to access hosting platforms and bug reports facilities.
\\
By allowing people to work collectively on projects using their native 
speaking language,
the NAME project will help the documentation translation and generaly the 
software documentation, that will facilitate a larger adoption of free/open
software in the mass of computer users that do not speak english.
\\

>>>>

To ensure the SICHA project dissemination it will be packaged so that 

@@

\chapter*{C4. Contribution to Community social objectives}
\addcontentsline{toc}{chapter}{C4. Contribution to Community social objectives}
\textit{This section, not exceeding two pages, should describe how the proposed
subject wil contribute to meeting the social objectives of the Community, and
should focus on the contribution of the project to improving employment
prospects and the use and development of skills in Europe. \\
Where aplicable the descriptions should also cover how the proposed measure
contributes to improving quality of life and health and safety (including
working condition), and/or to preserving or enhancing the environment and
natural ressources. This might include the contribution of the proposed work to
meeting relevant regulatory requirements.}
\\ \\
The SICHA project will help in creating more free/open software in EU by easing 
the access to a software hosting project platform.
\\
The software created using the hosting platforms, resulting from the SICHA 
project, will help reduce the software costs for individuals as well as for
small companies and large industrial groups. 
\\
The SICHA project will also strengthen existing software by allowing more 
developpers and testers to access hosting platforms and bug reports facilities.
\\
By allowing people to work collectively on projects using their native 
speaking language,
the SICHA project will help the documentation translation and generaly the 
software documentation, that will facilitate a larger adoption of free/open
software in the mass of computer users that do not speak english.
\\
